Adversarial Training against Systematic Uncertainty

### 2016-09-06 tex/paper.tex
save

Proposition~\ref{prop:2} suggests that if at each step of
Algorithm~\ref{alg:adversarial-training} the adversary $r$ is allowed to reach
its optimum given $f$ (e.g., by setting $K$ sufficiently high) and if $f$ is
updated to improve ${\cal L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$, then $f$
should converge to a classifier which is both optimal and pivotal, provided such
a classifier exists. On many problems of interest though, such a classifier may
not exist, in which case the lower bound $H(p_{Y|X}) - H(p_Z) < {\cal
L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$ is strict: $f$ can either be an optimal
classifier or a pivotal quantity, but not both simultaneously. Accordingly the value
function $E$ can be rewritten as
\begin{equation}
    E_\lambda(\theta_f, \theta_r) = {\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r),
\end{equation}
where $\lambda \geq 0$ is a hyper-parameter controlling the trade-off between the performance of $f$
and its independence with respect to the nuisance parameter. Setting $\lambda$ to a large
value will preferrably enforces $f$ to be pivotal while setting $\lambda$ to a value close to $0$
will rather constraint $f$ to be optimal.

>>>>

Proposition~\ref{prop:2} suggests that if at each step of
Algorithm~\ref{alg:adversarial-training} the adversary $r$ is allowed to reach
its optimum given $f$ (e.g., by setting $K$ sufficiently high) and if $f$ is
updated to improve ${\cal L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$, then $f$
should converge to a classifier which is both optimal and pivotal, provided such
a classifier exists. On many problems of interest though, such a classifier may
not exist because the nuisance parameter directly affects the optimal decision
boundary, in which cases the lower bound $H(p_{Y|X}) - H(p_Z) < {\cal
L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$ is strict: $f$ can either be an optimal
classifier or a pivotal quantity, but not both simultaneously. Accordingly the
value function $E$ can be rewritten as
\begin{equation}
    E_\lambda(\theta_f, \theta_r) = {\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r),
\end{equation}
where $\lambda \geq 0$ is a hyper-parameter controlling the trade-off between the performance of $f$
and its independence with respect to the nuisance parameter. Setting $\lambda$ to a large
value will preferrably enforces $f$ to be pivotal while setting $\lambda$ close to $0$
will rather constraint $f$ to be optimal.

\glnote{We should make it clearer what {\it classification optimality} means: it
is with respect to $Y|X=x$  when  $x$ results from $z\sim p_Z, x \sim X_z$.
This is often strictly different from optimality with respect to $Y|X=x,Z=z$ for the true value $z$.}
